---
title: "Sinangoe vs. Zabalo"
author: "Morgan Manning"
date: "2023-11-10"
output:
  html_document: default
  pdf_document: default
editor_options:
  markdown:
    wrap: 72
---

# Sinangoe versus Zabalo




```{r load packages, message=FALSE, warning=FALSE, include=FALSE}
require(unmarked)
require(dplyr)
require(ggplot2)
require(reshape2)
```

```{r Sinangoe, include=FALSE}
speciesDFs <- c(
  "SGEDicotylestajacu.csv",
  "SGEMazamaamericana.csv",
  "SGECuniculuspaca.csv",
  "SGEPsophiacrepitans.csv")

# read in all .csv files and remove any ID rows or columns 
dfList <- list()
for (i in 1:length(speciesDFs)) {
  species <- read.csv(paste0("../Data/", speciesDFs[i]))
  species <- species[,-1] # remove the column of ID names
  dfList[[i]] <- species
}

# name dfs after their associated species
# listTitlesSGE <- gsub('.csv', '', speciesDFs)
listTitlesSGE <- c("Collared peccary", "Red brocket", "Lowland paca", "Grey-winged trumpeter")
names(dfList) <- listTitlesSGE
speciesNames <- listTitlesSGE

# stations info
stations <- read.csv("../Data/SGEStationsFormatted.csv")
cameraRecords <- read.csv("../Data/SGEIndependentRecordsFormatted.csv")

# site covariates (scaled)
siteCovariateSGE <- data.frame(DistToComm = scale(stations$Community/1000))

# make all the data frames in the list into matrices
for (i in 1:length(dfList)) {
  dfList[[i]] <- dfList[[i]][ order(as.numeric(row.names(dfList[[i]]))), ] #order matters
  dfList[[i]] <- as.matrix(dfList[[i]])
}

# clump all matrices according to their best clumping factor
source("../../Zabalo/Scripts/optimalClumping.R")

clumpedMatrixList <- list()
for (i in 1:length(dfList)) {
  y <- dfList[[i]]
  clumpEvery <- as.numeric(best_clumping_factor(y)[1])
  nClumpedColumns <- ncol(y)/clumpEvery
  clumpedMatrix <- matrix(0, ncol = nClumpedColumns, nrow = nrow(y)) 
  
  clumpStart <- seq(1, ncol(y), by = clumpEvery) # the first column in the clump
  clumpEnd <- seq(clumpEvery, ncol(y), by = clumpEvery) # the last column in the clump
  
  ### make the clumped matrix
  for (k in 1:30){
    for (j in 1:ncol(clumpedMatrix)){
      if(all(is.na(y[k, clumpStart[j]:clumpEnd[j]])) == TRUE) {
        clumpedMatrix[k,j] <- NA
      } else if (sum(y[k, clumpStart[j]:clumpEnd[j]], na.rm=TRUE) >= 1) {
        clumpedMatrix[k,j] <- 1
      } else {
        clumpedMatrix[k,j] <- 0
      }
    }
  } # the clumped matrix is made
  clumpedMatrixList[[i]] <- clumpedMatrix
}
names(clumpedMatrixList) <- listTitlesSGE


# make unmarked df for each species
ufoList <- list()
for (i in 1:length(clumpedMatrixList)){
  clumpedMatrix <- clumpedMatrixList[[i]]
  ufo <- unmarkedFrameOccu(clumpedMatrix, 
                           siteCovs = siteCovariateSGE,
                           obsCovs = NULL)
  ufoList[[i]] <- ufo
}
names(ufoList) <- listTitlesSGE

# make unmarked df for each species without clumping
unclumpedUFOList <- list()
for (i in 1:length(dfList)){
  unclumpedMatrix <- dfList[[i]]
  ufo <- unmarkedFrameOccu(unclumpedMatrix, 
                           siteCovs = siteCovariateSGE,
                           obsCovs = NULL)
  unclumpedUFOList[[i]] <- ufo
}
names(unclumpedUFOList) <- listTitlesSGE

# make detection plots
# clumped
clumpPlotListSGE <- list()
for (i in 1:length(ufoList)) {
  ufo <- ufoList[[i]]
  colnames(ufo@y) <- 1:ncol(ufo@y)
  meltedComb <- melt(ufo@y)
  meltedComb$value <- as.factor(meltedComb$value)
  
  #plot
  clumpPlotListSGE[[i]] <- ggplot(meltedComb, aes(Var2, Var1, fill = value)) + 
    geom_tile(colour = "gray50") +
    scale_fill_manual(values=c("gray75", "red3"), na.value="white", name = "") +
    scale_x_continuous(breaks = seq(0, ncol(ufo@y), by = 2)) +
    scale_alpha_identity(guide = "none") +
    coord_equal(expand = 0) +
    xlab(paste("Time (1 unit = ~", 
               as.numeric(best_clumping_factor(dfList[[i]]))*2,
               # number of columns/time steps divided by the clumping factor, times 2
               "days)")) +
    ylab("Camera trap site") +
    ggtitle(gsub('SGE', '', listTitlesSGE[i])) +
    theme_bw() +
            theme(plot.title = element_text(size = 25, hjust = 0.5))
  
}

# unclumped
unclumpPlotListSGE <- list()
for (i in 1:length(unclumpedUFOList)) {
  ufo <- unclumpedUFOList[[i]]
  colnames(ufo@y) <- 1:ncol(ufo@y)
  meltedComb <- melt(ufo@y)
  meltedComb$value <- as.factor(meltedComb$value)
  
  #plot
  unclumpPlotListSGE[[i]] <- ggplot(meltedComb, aes(Var2, Var1, fill = value)) + 
    geom_tile(colour = "gray50") +
    scale_fill_manual(values=c("gray75", "red3"), na.value="white", name = "") +
    scale_x_continuous(breaks = seq(0, ncol(ufo@y), by = 2)) +
    scale_alpha_identity(guide = "none") +
    coord_equal(expand = 0) +
    xlab("Time (1 unit = 2 days)") +
    ylab("Camera trap site") +
    ggtitle(gsub('SGE', '', listTitlesSGE[i])) +
    theme_bw() +
            theme(plot.title = element_text(size = 25, hjust = 0.5))

  
}


############################################################################
############################## DETECTION ###################################
############################################################################

# vector of variables to consider for detection
match_variables <- c("1")

# every possible combination of variables
combos <- sapply( seq(length(match_variables)), function(i) {
  as.list(as.data.frame(combn( x = match_variables, m = i)))
})
combos <- unlist(combos, recursive=FALSE)

# all combinations of variables into formulas
forms <- sapply(combos, function(x) paste("~ ", paste(x, collapse="+"), sep = ""))

detectionFormulas <- as.vector(c(forms, "~ 1"))

# get the best detection formula and stick with that for the occupancy formulas
tempDF <- data.frame(detection = detectionFormulas,
                     occupancy = "~ 1")
allDetectionFormulas <- paste(tempDF$detection, tempDF$occupancy, sep = " ")

# see which detection model is the best
bestDetectionModels <- data.frame(species = listTitlesSGE,
                                  bestDetectionModel = NA)
for (j in 1:length(ufoList)) {
  detectionMods <- list()
  temp <- data.frame(Model = allDetectionFormulas,
                     AIC = NA)
  for(i in 1:length(allDetectionFormulas)) {
    test <- occu(formula(allDetectionFormulas[[i]]), ufoList[[j]])
    detectionMods[[i]] <- occu(formula(allDetectionFormulas[[i]]), ufoList[[j]], 
                               control = 10000, 
                               starts = c(rep(0, length(test@opt$par)))) 
    temp$AIC[i] <- detectionMods[[i]]@AIC
  }
  # select the model with the lowest AIC
  bestDetectionModels$bestDetectionModel[j] <- detectionFormulas[which(temp$AIC == min(temp$AIC))]
}




############################################################################
############################## OCCUPANCY ###################################
############################################################################

# vector of variables 
match_variables <- c("DistToComm")

# every possible combination of variables
combos <- sapply( seq(length(match_variables)), function(i) {
  as.list(as.data.frame(combn( x = match_variables, m = i)))
})
combos <- unlist(combos, recursive=FALSE)

# all combinations of variables into formulas
forms <- sapply(combos, function(x) paste("~ ", paste(x, collapse="+"), sep = ""))

forms <- as.vector(c(forms, "~ 1"))

occupancyFormulas <- forms


############################################################################
############################### MODELS #####################################
############################################################################
occupancyModelsList <- list()
for (i in 1:length(ufoList)) {
  df <- data.frame(detection = bestDetectionModels$bestDetectionModel[i],
                   occupancy = occupancyFormulas)
  occupancyModelsList[[i]] <- c(paste(df$detection, df$occupancy, sep = " "))
}

# run occupancy unmarked model for all models
allModelsSGE <- list()
for (j in 1:length(ufoList)) { # for all the species
  occupancyMods <- list()
  for(i in 1:length(occupancyModelsList[[j]])) {
    test <- occu(formula(occupancyModelsList[[j]][i]), ufoList[[j]])
    occupancyMods[[i]] <- occu(formula(occupancyModelsList[[j]][i]), ufoList[[j]], 
                               control = 10000, 
                               starts = c(rep(0, length(test@opt$par)))) 
  }
  names(occupancyMods) <- 1:length(occupancyMods)
  allModelsSGE[[j]] <- occupancyMods
}

# Make a data frame to show the model names and their AICs
modelAICs <- list()
topModelsSGE <- list() # only models within 2 AIC of lowest AIC
for(j in 1:length(allModelsSGE)) {
  df <- data.frame(ModelName = NA,
                   AIC = NA,
                   diffFromBest = NA)
  for(i in 1:length(allModelsSGE[[j]])){
    df[i,1]<- as.character(c(allModelsSGE[[j]][[i]]@formula))
    df[i,2]<- allModelsSGE[[j]][[i]]@AIC
  }
  df <- df[order(df$AIC),]
  df$diffFromBest <- df$AIC - min(df$AIC)
  modelAICs[[j]] <- df
  
  # only the best
  ANTM <- subset(df, diffFromBest <= 2)
  topModelsSGE[[j]] <- ANTM
}
names(topModelsSGE) <- listTitlesSGE

# take these best models and put them into a list
bestModsFitListsSGE <- list()
for (j in 1:length(topModelsSGE)){
  speciesBestMods <- list()
  for(i in 1:nrow(topModelsSGE[[j]])) {
    test <- occu(formula(topModelsSGE[[j]]$ModelName[i]), ufoList[[j]])
    
    speciesBestMods[[i]] <- occu(formula(topModelsSGE[[j]]$ModelName[i]), ufoList[[j]], 
                                 control = 10000, 
                                 starts = c(rep(0, length(test@opt$par)))) 
    #print(speciesBestMods[[i]])
  } 
  bestModsFitListsSGE[[j]] <- fitList(speciesBestMods)
}
names(bestModsFitListsSGE) <- listTitlesSGE

bestOfTheBestSGE <- list()
for (i in 1:length(listTitlesSGE)) {
  bestOfTheBestSGE[[i]] <- occu(formula(topModelsSGE[[i]]$ModelName[1]), ufoList[[i]])
}
names(bestOfTheBestSGE) <- listTitlesSGE


# OUTPUT: 
  # allModelsSGE
  # unclumpPlotListSGE
  # clumpPlotListSGE
  # bestModsFitListsSGE
  # topModelsSGE

```




```{r Zabalo, include = FALSE}
speciesDFs <- c(
  "ZABDicotylestajacu.csv",
  "ZABMazamaamericana.csv",
  "ZABCuniculuspaca.csv",
  "ZABPsophiacrepitans.csv")

###############################################################################
# read in all .csv files and remove any ID rows or columns 
dfList <- list()
for (i in 1:length(speciesDFs)) {
  species <- read.csv(paste0("../../Zabalo/Data/", speciesDFs[i]))
  species <- species[,-1] # remove the column of ID names
  dfList[[i]] <- species
}

# name dfs after their associated species
# listTitlesZAB <- gsub('.csv', '', speciesDFs)
listTitlesZAB <- c("Collared peccary", "Red brocket", "Lowland paca", "Grey-winged trumpeter")
names(dfList) <- listTitlesZAB
speciesNames <- listTitlesZAB

# Zabalo occupancy covariates
load('../../Zabalo/Data/R Objects/siteCovs2018.RData')
siteCovariateZAB <- siteCovariate

# stations and hunting info
stations <- read.csv("../../Zabalo/Data/Stations2018.csv")
hunting <- read.csv("../../Zabalo/Data/HuntingData2018.csv")
cameraRecords <- read.csv("../../Zabalo/Data/RecordTable2018.csv")


############################################################################
######################## FORMAT FOR UNMARKED ###############################
############################################################################

# make all the data frames in the list into matrices
for (i in 1:length(dfList)) {
  dfList[[i]] <- dfList[[i]][ order(as.numeric(row.names(dfList[[i]]))), ] #order matters
  dfList[[i]] <- as.matrix(dfList[[i]])
}


# clump all matrices according to their best clumping factor
source("../../Zabalo/Scripts/optimalClumping.R")

clumpedMatrixList <- list()
for (i in 1:length(dfList)) {
  y <- dfList[[i]]
  clumpEvery <- as.numeric(best_clumping_factor(y))
  nClumpedColumns <- ncol(y)/clumpEvery
  clumpedMatrix <- matrix(0, ncol = nClumpedColumns, nrow = nrow(y)) 
  
  clumpStart <- seq(1, ncol(y), by = clumpEvery) # the first column in the clump
  clumpEnd <- seq(clumpEvery, ncol(y), by = clumpEvery) # the last column in the clump
  
  ### make the clumped matrix
  for (k in 1:30){
    for (j in 1:ncol(clumpedMatrix)){
      if(all(is.na(y[k, clumpStart[j]:clumpEnd[j]])) == TRUE) {
        clumpedMatrix[k,j] <- NA
      } else if (sum(y[k, clumpStart[j]:clumpEnd[j]], na.rm=TRUE) >= 1) {
        clumpedMatrix[k,j] <- 1
      } else {
        clumpedMatrix[k,j] <- 0
      }
    }
  } # the clumped matrix is made
  clumpedMatrixList[[i]] <- clumpedMatrix
}
names(clumpedMatrixList) <- listTitlesZAB


# make unmarked df for each species
ufoList <- list()
for (i in 1:length(clumpedMatrixList)){
  clumpedMatrix <- clumpedMatrixList[[i]]
  ufo <- unmarkedFrameOccu(clumpedMatrix, 
                           siteCovs = siteCovariateZAB,
                           obsCovs = NULL)
  ufoList[[i]] <- ufo
}
names(ufoList) <- listTitlesZAB

# make unmarked df for each species without clumping
unclumpedUFOList <- list()
for (i in 1:length(dfList)){
  unclumpedMatrix <- dfList[[i]]
  ufo <- unmarkedFrameOccu(unclumpedMatrix, 
                           siteCovs = siteCovariateZAB,
                           obsCovs = NULL)
  unclumpedUFOList[[i]] <- ufo
}
names(unclumpedUFOList) <- listTitlesZAB

# make detection plots
# clumped
clumpPlotListZAB <- list()
for (i in 1:length(ufoList)) {
  ufo <- ufoList[[i]]
  colnames(ufo@y) <- 1:ncol(ufo@y)
  meltedComb <- melt(ufo@y)
  meltedComb$value <- as.factor(meltedComb$value)
  
  #plot
  clumpPlotListZAB[[i]] <- ggplot(meltedComb, aes(Var2, Var1, fill = value)) + 
    geom_tile(colour = "gray50") +
    scale_fill_manual(values=c("gray75", "red3"), na.value="white", name = "") +
    scale_x_continuous(breaks = seq(0, ncol(ufo@y), by = 2)) +
    scale_alpha_identity(guide = "none") +
    coord_equal(expand = 0) +
    xlab(paste("Time (1 unit = ~", 
               as.numeric(best_clumping_factor(dfList[[i]]))*2,
               # number of columns/time steps divided by the clumping factor, times 2
               "days)")) +
    ylab("Camera trap site") +
        ggtitle(gsub('ZAB', '', listTitlesZAB[i])) +
    theme_bw()+
            theme(plot.title = element_text(size = 25, hjust = 0.5))
}

# unclumped
unclumpPlotListZAB <- list()
for (i in 1:length(unclumpedUFOList)) {
  ufo <- unclumpedUFOList[[i]]
  colnames(ufo@y) <- 1:ncol(ufo@y)
  meltedComb <- melt(ufo@y)
  meltedComb$value <- as.factor(meltedComb$value)
  
  #plot
  unclumpPlotListZAB[[i]] <- ggplot(meltedComb, aes(Var2, Var1, fill = value)) + 
    geom_tile(colour = "gray50") +
    scale_fill_manual(values=c("gray75", "red3"), na.value="white", name = "") +
    scale_x_continuous(breaks = seq(0, ncol(ufo@y), by = 2)) +
    scale_alpha_identity(guide = "none") +
    coord_equal(expand = 0) +
    xlab("Time (1 unit = 2 days)") +
    ylab("Camera trap site") +
    ggtitle(gsub('ZAB', '', listTitlesZAB[i])) +
    theme_bw() +
    theme(plot.title = element_text(size = 25, hjust = 0.5))
  
}


############################################################################
############################## DETECTION ###################################
############################################################################

# vector of variables to consider for detection
match_variables <- c("Effort", "Habitat")

# every possible combination of variables
combos <- sapply( seq(length(match_variables)), function(i) {
  as.list(as.data.frame(combn( x = match_variables, m = i)))
})
combos <- unlist(combos, recursive=FALSE)

# all combinations of variables into formulas
forms <- sapply(combos, function(x) paste("~ ", paste(x, collapse="+"), sep = ""))

detectionFormulas <- as.vector(c(forms, "~ 1"))

# get the best detection formula and stick with that for the occupancy formulas
tempDF <- data.frame(detection = detectionFormulas,
                     occupancy = "~ 1")
allDetectionFormulas <- paste(tempDF$detection, tempDF$occupancy, sep = " ")

# see which detection model is the best
bestDetectionModels <- data.frame(species = listTitlesZAB,
                                  bestDetectionModel = NA)
for (j in 1:length(ufoList)) {
  detectionMods <- list()
  temp <- data.frame(Model = allDetectionFormulas,
                     AIC = NA)
  for(i in 1:length(allDetectionFormulas)) {
    test <- occu(formula(allDetectionFormulas[[i]]), ufoList[[j]])
    detectionMods[[i]] <- occu(formula(allDetectionFormulas[[i]]), ufoList[[j]], 
                               control = 10000, 
                               starts = c(rep(0, length(test@opt$par)))) 
    temp$AIC[i] <- detectionMods[[i]]@AIC
  }
  # select the model with the lowest AIC
  bestDetectionModels$bestDetectionModel[j] <- detectionFormulas[which(temp$AIC == min(temp$AIC))]
  }



############################################################################
############################## OCCUPANCY ###################################
############################################################################

# vector of variables 
match_variables <- c("Habitat", "Trail.Distance", "HuntingIntensity")

# every possible combination of variables
combos <- sapply( seq(length(match_variables)), function(i) {
  as.list(as.data.frame(combn( x = match_variables, m = i)))
})
combos <- unlist(combos, recursive=FALSE)

# all combinations of variables into formulas
forms <- sapply(combos, function(x) paste("~ ", paste(x, collapse="+"), sep = ""))

forms <- as.vector(c(forms, "~ 1"))

occupancyFormulas <- forms


############################################################################
############################### MODELS #####################################
############################################################################
occupancyModelsList <- list()
for (i in 1:length(ufoList)) {
  df <- data.frame(detection = bestDetectionModels$bestDetectionModel[i],
                                         occupancy = occupancyFormulas)
  occupancyModelsList[[i]] <- c(paste(df$detection, df$occupancy, sep = " "))
  }

# run occupancy unmarked model for all models
allModels <- list()
for (j in 1:length(ufoList)) { # for all the species
  occupancyMods <- list()
  for(i in 1:length(occupancyModelsList[[j]])) {
    test <- occu(formula(occupancyModelsList[[j]][i]), ufoList[[j]])
    occupancyMods[[i]] <- occu(formula(occupancyModelsList[[j]][i]), ufoList[[j]], 
                               control = 10000, 
                               starts = c(rep(0, length(test@opt$par)))) 
  }
  names(occupancyMods) <- 1:length(occupancyMods)
  allModels[[j]] <- occupancyMods
}


# remove all models with missing SE/z/p-value or that didn't converge
noMissingMods <- list()
for(j in 1:length(allModels)) {
  eachSpecies <- list()
  for(i in 1:length(allModels[[j]])){
    
    modSum <- summary(allModels[[j]][[i]])
    
    if(anyNA(modSum$state$SE)==FALSE & allModels[[j]][[i]]@opt$convergence != 1){
      eachSpecies[[i]] <- allModels[[j]][[i]]
    } else {
      next
    }
  }
  eachSpecies[sapply(eachSpecies, is.null)] <- NULL
  noMissingMods[[j]] <- eachSpecies
}

# remove all models with ridiculous standard errors
noWackyMods <- list()
for(j in 1:length(noMissingMods)) {
  eachSpecies <- list()
  for(i in 1:length(noMissingMods[[j]])){
    
    modSum <- summary(noMissingMods[[j]][[i]])
    
    if((abs(modSum$state$SE[1]) < modSum$state$Estimate[1]) == TRUE){
      eachSpecies[[i]] <- noMissingMods[[j]][[i]]
    } else {
      next
    }
  }
  eachSpecies[sapply(eachSpecies, is.null)] <- NULL
  noWackyMods[[j]] <- eachSpecies
}
names(noWackyMods) <- listTitlesZAB

# noWackyMods

# Make a data frame to show the model names and their AICs
modelAICs <- list()
topModelsZAB <- list() # only models within 2 AIC of lowest AIC
for(j in 1:length(noWackyMods)) {
  df <- data.frame(ModelName = NA,
                   AIC = NA,
                   diffFromBest = NA)
  for(i in 1:length(noWackyMods[[j]])){
    df[i,1]<- as.character(c(noWackyMods[[j]][[i]]@formula))
    df[i,2]<- noWackyMods[[j]][[i]]@AIC
  }
  df <- df[order(df$AIC),]
  df$diffFromBest <- df$AIC - min(df$AIC)
  modelAICs[[j]] <- df
  
  # only the best
  ANTM <- subset(df, diffFromBest <= 2)
  topModelsZAB[[j]] <- ANTM
}
names(topModelsZAB) <- listTitlesZAB

# take these best models and put them into a list
bestModsFitListsZAB <- list()
for (j in 1:length(topModelsZAB)){
  speciesBestMods <- list()
  for(i in 1:nrow(topModelsZAB[[j]])) {
    test <- occu(formula(topModelsZAB[[j]]$ModelName[i]), ufoList[[j]])
    
    speciesBestMods[[i]] <- occu(formula(topModelsZAB[[j]]$ModelName[i]), ufoList[[j]], 
                          control = 10000, 
                          starts = c(rep(0, length(test@opt$par)))) 
    #print(speciesBestMods[[i]])
  } 
  bestModsFitListsZAB[[j]] <- fitList(speciesBestMods)
}
names(bestModsFitListsZAB) <- listTitlesZAB

bestOfTheBestZAB <- list()
for (i in 1:length(listTitlesZAB)) {
  bestOfTheBestZAB[[i]] <- occu(formula(topModelsZAB[[i]]$ModelName[1]), ufoList[[i]])
}
names(bestOfTheBestZAB) <- listTitlesZAB

# OUTPUT:
  # clumpPlotListZAB
  # unclumpPlotListZAB
  # noWackyMods
  # bestModsFitListsZAB
  # topModelsZAB

```


```{r record tables, include=FALSE}
indivRecordsZAB <- read.csv("../../Zabalo/Data/ZABIndependentRecordsFormatted.csv")
indivRecordsSGE <- read.csv("../Data/SGEIndependentRecordsFormatted.csv")

indivRecordsSNA <- read.csv("../../Siona/Data/SNAIndependentRecordsFormatted.csv")
indivRecordsSKP <- read.csv("../../Siekopai/Data/SKPIndependentRecordsFormatted.csv")

```

## Timeframe

In Zabalo, camera trapping commenced on `r min(indivRecordsZAB$Date)`
and ended on `r max(indivRecordsZAB$Date)`, spanning
`r as.numeric(as.Date(max(indivRecordsZAB$Date)) - as.Date(min(indivRecordsZAB$Date)))`
days. As for Sinangoe, trapping began on
`r as.Date(min(indivRecordsSGE$Date))` and ended on
`r as.Date(max(indivRecordsSGE$Date))`, going for
`r as.numeric(as.Date(max(indivRecordsSGE$Date)) - as.Date(min(indivRecordsSGE$Date)))`
days.

\

------------------------------------------------------------------------

## Consolidating time steps
The following plots show unconsolidated versus consolidated time steps
for three species in Sinangoe and in Zabalo.

### Sinangoe

```{r plot Sinangoe clumped vs unclumped, echo=FALSE, fig.show="hold", out.width="25%"}
par( mfrow= c(4, 2) )
plot(unclumpPlotListSGE[[1]]); plot(unclumpPlotListSGE[[2]]); plot(unclumpPlotListSGE[[3]]); plot(unclumpPlotListSGE[[4]]); plot(clumpPlotListSGE[[1]]); plot(clumpPlotListSGE[[2]]); plot(clumpPlotListSGE[[3]]); plot(clumpPlotListSGE[[4]])

```

\

### Zabalo

```{r plot Zabalo clumped vs unclumped, echo=FALSE, fig.show="hold", out.width="25%"}
par( mfrow= c(4, 2) )
plot(unclumpPlotListZAB[[1]]); plot(unclumpPlotListZAB[[2]]); plot(unclumpPlotListZAB[[3]]); plot(unclumpPlotListZAB[[4]]); plot(clumpPlotListZAB[[1]]); plot(clumpPlotListZAB[[2]]); plot(clumpPlotListZAB[[3]]); plot(clumpPlotListZAB[[4]])

```

\

\
  

------------------------------------------------------------------------


## Top species

### Zabalo

```{r, echo=FALSE}
# explore total detections
total <- data.frame(table(indivRecordsZAB$Species)) # number of detections / species
colnames(total) <- c("Species", "Total")
knitr::kable(head(total[order(-total$Total),], 15), format="markdown", caption = "Zabalo Species")
```


### Sinangoe
```{r, echo=FALSE}

# explore total detections
total <- data.frame(table(indivRecordsSGE$Species)) # number of detections / species
colnames(total) <- c("Species", "Total")
knitr::kable(head(total[order(-total$Total),], 15), format="markdown", caption = "Sinangoe Species")


```

  \
  
  \

------------------------------------------------------------------------


## Occupancy modeling

Proceeding with all models for Sinangoe and models without missing
estimates or disproportionately large standard errors for Zabalo.

\

### Zabalo

```{r Zabalo models, echo=FALSE}
# OUTPUT:
  # bestModsFitListsZAB
  # topModelsZAB
knitr::kable(topModelsZAB[[1]], format="markdown", caption = names(topModelsZAB)[1])
knitr::kable(topModelsZAB[[2]], format="markdown", caption = names(topModelsZAB)[2])
knitr::kable(topModelsZAB[[3]], format="markdown", caption = names(topModelsZAB)[3])
knitr::kable(topModelsZAB[[4]], format="markdown", caption = names(topModelsZAB)[4])

```

\

#### Top Models

##### `r gsub('ZAB', '', names(bestOfTheBestZAB)[1])`

```{r, echo=FALSE}
bestOfTheBestZAB[[1]]@estimates
```

##### `r gsub('ZAB', '', names(bestOfTheBestZAB)[2])`

```{r, echo=FALSE}
bestOfTheBestZAB[[2]]@estimates
```

##### `r gsub('ZAB', '', names(bestOfTheBestZAB)[3])`

```{r, echo=FALSE}
bestOfTheBestZAB[[3]]@estimates
```

##### `r gsub('ZAB', '', names(bestOfTheBestZAB)[4])`

```{r, echo=FALSE}
bestOfTheBestZAB[[4]]@estimates
```

\

### Sinangoe

```{r Sinangoe models, echo=FALSE}
# OUTPUT: 
  # bestModsFitListsSGE
  # topModelsSGE
knitr::kable(topModelsSGE[[1]], format="markdown", caption = names(topModelsSGE)[1])
knitr::kable(topModelsSGE[[2]], format="markdown", caption = names(topModelsSGE)[2])
knitr::kable(topModelsSGE[[3]], format="markdown", caption = names(topModelsSGE)[3])
knitr::kable(topModelsSGE[[4]], format="markdown", caption = names(topModelsSGE)[4])

```

\

#### Top Models
##### `r gsub('SGE', '', names(bestOfTheBestSGE)[1])`

```{r, echo=FALSE}
bestOfTheBestSGE[[1]]@estimates
```

##### `r gsub('SGE', '', names(bestOfTheBestSGE)[2])`

```{r, echo=FALSE}
bestOfTheBestSGE[[2]]@estimates
```


##### `r gsub('SGE', '', names(bestOfTheBestSGE)[3])`

```{r, echo=FALSE}
bestOfTheBestSGE[[3]]@estimates
```

##### `r gsub('SGE', '', names(bestOfTheBestSGE)[4])`

```{r, echo=FALSE}
bestOfTheBestSGE[[4]]@estimates
```

\

\



------------------------------------------------------------------------

## Diversity and richness

#### Species richness
Zabalo and Sinangoe had `r (nrow(data.frame(table(indivRecordsZAB$Species)))-1)` and `r (nrow(data.frame(table(indivRecordsSGE$Species)))-1)` total species, respectively, with Menhinick's species richness indices of `r round((nrow(data.frame(table(indivRecordsZAB$Species)))-1)/(sqrt(sum(data.frame(table(indivRecordsZAB$Species))[,2]))), 3)` and `r round((nrow(data.frame(table(indivRecordsSGE$Species)))-1)/(sqrt(sum(data.frame(table(indivRecordsSGE$Species))[,2]))), 3)`. 

\

#### Diversity
```{r, include=FALSE}
noUnknownsSGE <- indivRecordsSGE[indivRecordsSGE$Species != "N/D N/D",]
noUnknownsZAB <- indivRecordsZAB[(indivRecordsZAB$Species != "NAN NAN" & indivRecordsZAB$Species != "NA NA"),]
noUnknownsSNA <- indivRecordsSNA[indivRecordsSNA$Species != "N/D N/D",]
noUnknownsSKP <- indivRecordsSKP[indivRecordsSKP$Species != "N/D N/D",]

# per station
  # Sinangoe
siteDiversitySGE <- noUnknownsSGE %>%
  group_by(Station, Species) %>%
  summarise(abundance = n()) 

siteDiversitySGE <- siteDiversitySGE %>%
  group_by(Station) %>%
  summarise(N=sum(abundance),
            shannonDiversity = -sum((abundance/sum(abundance))*log(abundance/sum(abundance))),
            simpsonDiversity = 1-sum((abundance/sum(abundance))^2))

# Zabalo
siteDiversityZAB <- noUnknownsZAB %>%
  group_by(Station, Species) %>%
  summarise(abundance = n()) 

siteDiversityZAB <- siteDiversityZAB %>%
  group_by(Station) %>%
  summarise(N=sum(abundance),
            shannonDiversity = -sum((abundance/sum(abundance))*log(abundance/sum(abundance))),
            simpsonDiversity = 1-sum((abundance/sum(abundance))^2))

# Siona
siteDiversitySNA <- noUnknownsSNA %>%
  group_by(Station, Species) %>%
  summarise(abundance = n()) 

siteDiversitySNA <- siteDiversitySNA %>%
  group_by(Station) %>%
  summarise(N=sum(abundance),
            shannonDiversity = -sum((abundance/sum(abundance))*log(abundance/sum(abundance))),
            simpsonDiversity = 1-sum((abundance/sum(abundance))^2))

# Siekopai
siteDiversitySKP <- noUnknownsSKP %>%
  group_by(Station, Species) %>%
  summarise(abundance = n()) 

siteDiversitySKP <- siteDiversitySKP %>%
  group_by(Station) %>%
  summarise(N=sum(abundance),
            shannonDiversity = -sum((abundance/sum(abundance))*log(abundance/sum(abundance))),
            simpsonDiversity = 1-sum((abundance/sum(abundance))^2))

```


```{r include=FALSE}
# per community
wholeDiversitySGE <- noUnknownsSGE %>%
  group_by(Species) %>%
  summarise(abundance = n()) %>%
  mutate(Community = "Sinangoe")
wholeDiversityZAB <- noUnknownsZAB %>%
  group_by(Species) %>%
  summarise(abundance = n()) %>%
  mutate(Community = "Zabalo")
wholeDiversitySNA <- noUnknownsSNA %>%
  group_by(Species) %>%
  summarise(abundance = n()) %>%
  mutate(Community = "Siona")
wholeDiversitySKP <- noUnknownsSKP %>%
  group_by(Species) %>%
  summarise(abundance = n()) %>%
  mutate(Community = "Siekopai")

communityAbundance <- rbind(wholeDiversitySGE, wholeDiversityZAB, wholeDiversitySNA, wholeDiversitySKP)
communityDiversity <- communityAbundance %>%
  group_by(Community) %>%
  summarise(nIndiv=sum(abundance),
            nSpecies = length(unique(Species)),
            shannonIndex = -sum((abundance/sum(abundance))*log(abundance/sum(abundance))),
            simpsonIndex = 1-sum((abundance/sum(abundance))^2))

```
Among Sinangoe stations, the Shannon Diversity Index ranged from `r round(min(siteDiversitySGE$shannonDiversity), 3)` to `r round(max(siteDiversitySGE$shannonDiversity), 3)`. Among Zabalo stations, the Shannon Diversity Index ranged from `r round(min(siteDiversityZAB$shannonDiversity), 3)` to `r round(max(siteDiversityZAB$shannonDiversity), 3)`. Among Siona stations, the Shannon Diversity Index ranged from `r round(min(siteDiversitySNA$shannonDiversity), 3)` to `r round(max(siteDiversitySNA$shannonDiversity), 3)`.
Among Siekopai stations, the Shannon Diversity Index ranged from `r round(min(siteDiversitySKP$shannonDiversity), 3)` to `r round(max(siteDiversitySKP$shannonDiversity), 3)`.

```{r echo=FALSE}
knitr::kable(communityDiversity, format="markdown", caption = "Species Diversity")
```



\


\

------------------------------------------------------------------------

## Occupancy predictions

### Sinangoe
```{r include=FALSE}
speciesNames <- listTitlesSGE

commDF <- data.frame(
  DistToComm = seq(min(siteCovariateSGE$DistToComm), 
                   max(siteCovariateSGE$DistToComm), 
                   length.out = 100)
) 

# predict
commPredictionsSGE <- list()
for (j in 1:length(bestModsFitListsSGE)) {
  mods <- bestModsFitListsSGE[[j]]
  unmarkedPred <- predict(mods, type = 'state', new = commDF, appendData = TRUE)
  predictionDataFrame <- data.frame(Predicted = unmarkedPred$Predicted,
                                    lower = unmarkedPred$lower,
                                    upper = unmarkedPred$upper,
                                    commDF)
  commPredictionsSGE[[j]] <- predictionDataFrame
}
names(commPredictionsSGE) <- listTitlesSGE

# get limits of covariates for each species (for plotting)
xLimits <- data.frame(species = speciesNames,
                      commMinX = NA,
                      commMaxX = NA)
for (j in 1:length(speciesNames)) {
  speciesCommPrediction <- commPredictionsSGE[[j]]
  xLimits[j,"commMinX"] <- min(speciesCommPrediction$DistToComm)
  xLimits[j,"commMaxX"] <- max(speciesCommPrediction$DistToComm)
}


###### PLOT IT

commPlots <- list()

for (j in 1:length(speciesNames)) {
  # Hunting intensity
  speciesCommPrediction <- commPredictionsSGE[[j]]
  commPlots[[j]] <- ggplot(speciesCommPrediction, 
                           aes(x = DistToComm, y = Predicted)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), 
                fill = 'red', alpha = 0.5, linetype = "dashed") +
    geom_path(linewidth = 1) +
    labs(x = "Distance to community (scaled)", y = "Occupancy probability") +
    ggtitle(label = speciesNames[j]) +
    theme_classic() +
    coord_cartesian(ylim = c(0,1), 
                    xlim = c(xLimits[j,"commMinX"], xLimits[j,"commMaxX"])) +
    theme(text = element_text(family = "Times", colour = "black"),
          axis.text = element_text(colour = "black"),
          plot.title = element_text(hjust = 0.5),
          plot.subtitle = element_text(hjust = 0.5, face = 'italic'))
}

```

```{r echo=FALSE, fig.show="hold", out.width="25%"}
par(mfrow= c(4, 1))
plot(commPlots[[1]]) ; plot(commPlots[[2]]) ; plot(commPlots[[3]]) ; plot(commPlots[[4]])
```


### Zabalo
```{r include=FALSE}
speciesNames <- listTitlesZAB
############### TRAIL DISTANCE ##################
# First, set-up a new data frame to predict along a sequence of the covariate.
# Predicting requires all covariates, so hold the other covariates constant at their mean value
trailDF <- data.frame(
                 Habitat = as.factor("Upland"), # most common habitat
                 Trail.Distance = seq(min(siteCovariateZAB$Trail.Distance), 
                                      max(siteCovariateZAB$Trail.Distance), 
                                      length.out = 100),
                 HuntingIntensity = mean(siteCovariateZAB$HuntingIntensity)
) 

# predict
trailPredictions <- list()
for (j in 1:length(bestModsFitListsZAB)) {
  mods <- bestModsFitListsZAB[[j]]
  unmarkedPred <- predict(mods, type = 'state', new = trailDF, appendData = TRUE)
  predictionDataFrame <- data.frame(Predicted = unmarkedPred$Predicted,
                                    lower = unmarkedPred$lower,
                                    upper = unmarkedPred$upper,
                                    trailDF)
  trailPredictions[[j]] <- predictionDataFrame
}
names(trailPredictions) <- listTitlesZAB


############### HUNTING INTENSITY ##################
# First, set-up a new data frame to predict along a sequence of the covariate.
# Predicting requires all covariates, so hold the other covariates constant at their mean value
huntingDF <- data.frame(
                 Habitat = as.factor("Upland"), # most common habitat
                 Trail.Distance = mean(siteCovariateZAB$Trail.Distance),
                 HuntingIntensity = seq(min(siteCovariateZAB$HuntingIntensity), 
                                        max(siteCovariateZAB$HuntingIntensity), 
                                        length.out = 100)
) 

# predict
huntingPredictions <- list()
for (j in 1:length(bestModsFitListsZAB)) {
  mods <- bestModsFitListsZAB[[j]]
  unmarkedPred <- predict(mods, type = 'state', new = huntingDF, appendData = TRUE)
  predictionDataFrame <- data.frame(Predicted = unmarkedPred$Predicted,
                                    lower = unmarkedPred$lower,
                                    upper = unmarkedPred$upper,
                                    huntingDF)
  huntingPredictions[[j]] <- predictionDataFrame
}
names(huntingPredictions) <- listTitlesZAB



######### ACTUALLY PLOTTING ###########
huntingPlots <- list()
trailPlots <- list()
# get limits of covariates for each species (for plotting)
xLimits <- data.frame(species = speciesNames,
                      trailMinX = NA,
                      trailMaxX = NA,
                      huntingMinX = NA,
                      huntingMaxX = NA)
for (j in 1:length(speciesNames)) {
  speciesTrailPrediction <- trailPredictions[[j]]
  xLimits[j,"trailMinX"] <- min(speciesTrailPrediction$Trail.Distance)
  xLimits[j,"trailMaxX"] <- max(speciesTrailPrediction$Trail.Distance)
  
  speciesHuntingPrediction <- huntingPredictions[[j]]
  xLimits[j,"huntingMinX"] <- min(speciesHuntingPrediction$HuntingIntensity)
  xLimits[j,"huntingMaxX"] <- max(speciesHuntingPrediction$HuntingIntensity)

}


# make a plot for hunting intensity and trail distance for each species j
for (j in 1:length(speciesNames)) {
  
  # Distance to a trail prediction
  speciesTrailPrediction <- trailPredictions[[j]]
  trailPlots[[j]] <- ggplot(speciesTrailPrediction, aes(x = Trail.Distance, y = Predicted)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), fill = 'green4', alpha = 0.5, linetype = "dashed") +
    geom_path(linewidth = 1) +
    labs(x = "Distance to a trail (scaled)", y = "Occupancy probability") +
    ggtitle(label = speciesNames[j]) +
    theme_classic() +
    coord_cartesian(ylim = c(0,1), xlim = c(xLimits[j,"trailMinX"], xLimits[j,"trailMaxX"])) +
    theme(text = element_text(family = "Times", colour = "black"),
          axis.text = element_text(colour = "black"),
          plot.title = element_text(hjust = 0.5),
          plot.subtitle = element_text(hjust = 0.5, face = 'italic'))
  
  
  # Hunting intensity
  speciesHuntingPrediction <- huntingPredictions[[j]]
  huntingPlots[[j]] <- ggplot(speciesHuntingPrediction, aes(x = HuntingIntensity, y = Predicted)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), fill = 'orange', alpha = 0.5, linetype = "dashed") +
    geom_path(linewidth = 1) +
    labs(x = "Hunting intensity (scaled)", y = "Occupancy probability") +
    ggtitle(label = speciesNames[j]) +
    theme_classic() +
    coord_cartesian(ylim = c(0,1), xlim = c(xLimits[j,"huntingMinX"], xLimits[j,"huntingMaxX"])) +
    theme(text = element_text(family = "Times", colour = "black"),
          axis.text = element_text(colour = "black"),
          plot.title = element_text(hjust = 0.5),
          plot.subtitle = element_text(hjust = 0.5, face = 'italic'))
 
}

```

```{r echo=FALSE, fig.show="hold", out.width="25%"}
par( mfrow= c(3, 2) )
plot(huntingPlots[[1]]); plot(huntingPlots[[2]]); plot(huntingPlots[[3]]); plot(huntingPlots[[4]]); plot(trailPlots[[1]]); plot(trailPlots[[2]]); plot(trailPlots[[3]]); plot(trailPlots[[4]])
```



\


\

------------------------------------------------------------------------

## Occupancy and detection estimates
Occupancy and detection are averaged across sites using actual covariate values as input.

\

### Sinangoe

```{r include=FALSE}
df <- data.frame(
  DistToComm = siteCovariateSGE$DistToComm) 

estimatedParameters <- list()
unmarkedPredOccSGE <- list()
unmarkedPredDetSGE <- list()
for (j in 1:length(bestModsFitListsSGE)) {
  # state = occupancy
  unmarkedPredOccSGE[[j]] <- predict(bestModsFitListsSGE[[j]], type = 'state', new = df, appendData = TRUE)
  # det = detection
  unmarkedPredDetSGE[[j]] <- predict(bestModsFitListsSGE[[j]], type = 'det', new = df, appendData = TRUE)
  estimatedParameters[[j]] <- data.frame(avgOccupancy = mean(unmarkedPredOccSGE[[j]]$Predicted),
                                         avgOccupancySE = mean(unmarkedPredOccSGE[[j]]$SE),
                                         occupancyRange = range(unmarkedPredOccSGE[[j]]$Predicted),
                                         avgDetection = mean(unmarkedPredDetSGE[[j]]$Predicted),
                                         avgDetectionSE = mean(unmarkedPredDetSGE[[j]]$SE),
                                         detectionRange = range(unmarkedPredDetSGE[[j]]$Predicted))
}
names(estimatedParameters) <- listTitlesSGE
names(unmarkedPredOccSGE) <- listTitlesSGE
names(unmarkedPredDetSGE) <- listTitlesSGE


```

```{r echo=FALSE}
detOccSGE <- data.frame(Species = listTitlesZAB,
           avgOccupancy = c(estimatedParameters[[listTitlesZAB[1]]]$avgOccupancy[1],
                            estimatedParameters[[listTitlesZAB[2]]]$avgOccupancy[1],
                            estimatedParameters[[listTitlesZAB[3]]]$avgOccupancy[1],
                            estimatedParameters[[listTitlesZAB[4]]]$avgOccupancy[1]),
           
           avgOccupancySE = c(estimatedParameters[[listTitlesZAB[1]]]$avgOccupancySE[1],
                            estimatedParameters[[listTitlesZAB[2]]]$avgOccupancySE[1],
                            estimatedParameters[[listTitlesZAB[3]]]$avgOccupancySE[1],
                            estimatedParameters[[listTitlesZAB[4]]]$avgOccupancySE[1]),
           
           avgDetection = c(estimatedParameters[[listTitlesZAB[1]]]$avgDetection[1],
                            estimatedParameters[[listTitlesZAB[2]]]$avgDetection[1],
                            estimatedParameters[[listTitlesZAB[3]]]$avgDetection[1],
                            estimatedParameters[[listTitlesZAB[4]]]$avgDetection[1]),
           
           avgDetectionSE = c(estimatedParameters[[listTitlesZAB[1]]]$avgDetectionSE[1],
                            estimatedParameters[[listTitlesZAB[2]]]$avgDetectionSE[1],
                            estimatedParameters[[listTitlesZAB[3]]]$avgDetectionSE[1],
                            estimatedParameters[[listTitlesZAB[4]]]$avgDetectionSE[1]))

knitr::kable(detOccSGE, format="markdown", caption = "Sinangoe occupancy and detection estimates")
# save(detOccSGE, file = "../Data/R Objects/detOccEstimatesSGE.RData")

```








### Zabalo
```{r include=FALSE}
###### average occupancy and detection across sites
# Model-averaged prediction of occupancy and confidence interval

df <- data.frame(
  Habitat = siteCovariateZAB$Habitat,
  HuntingIntensity = siteCovariateZAB$HuntingIntensity,
  Trail.Distance = siteCovariateZAB$Trail.Distance,
  Effort = siteCovariateZAB$Effort
) 

estimatedParameters <- list()
unmarkedPredOccZAB <- list()
unmarkedPredDetZAB <- list()
for (j in 1:length(bestModsFitListsZAB)) {
  # state = occupancy
  unmarkedPredOccZAB[[j]] <- unmarked::predict(bestModsFitListsZAB[[j]], type = 'state', new = df, appendData = TRUE)
  # det = detection
  unmarkedPredDetZAB[[j]] <- unmarked::predict(bestModsFitListsZAB[[j]], type = 'det', new = df, appendData = TRUE)
  estimatedParameters[[j]] <- data.frame(avgOccupancy = mean(unmarkedPredOccZAB[[j]]$Predicted),
                                         avgOccupancySE = mean(unmarkedPredOccZAB[[j]]$SE),
                                         occupancyRange = range(unmarkedPredOccZAB[[j]]$Predicted),
                                         avgDetection = mean(unmarkedPredDetZAB[[j]]$Predicted),
                                         avgDetectionSE = mean(unmarkedPredDetZAB[[j]]$SE),
                                         detectionRange = range(unmarkedPredDetZAB[[j]]$Predicted))
}
names(estimatedParameters) <- listTitlesZAB
names(unmarkedPredOccZAB) <- listTitlesZAB
names(unmarkedPredDetZAB) <- listTitlesZAB


```

```{r echo=FALSE}
detOccZAB <- data.frame(Species = listTitlesZAB,
           avgOccupancy = c(estimatedParameters[[listTitlesZAB[1]]]$avgOccupancy[1],
                            estimatedParameters[[listTitlesZAB[2]]]$avgOccupancy[1],
                            estimatedParameters[[listTitlesZAB[3]]]$avgOccupancy[1],
                            estimatedParameters[[listTitlesZAB[4]]]$avgOccupancy[1]),
           
           avgOccupancySE = c(estimatedParameters[[listTitlesZAB[1]]]$avgOccupancySE[1],
                            estimatedParameters[[listTitlesZAB[2]]]$avgOccupancySE[1],
                            estimatedParameters[[listTitlesZAB[3]]]$avgOccupancySE[1],
                            estimatedParameters[[listTitlesZAB[4]]]$avgOccupancySE[1]),
           
           avgDetection = c(estimatedParameters[[listTitlesZAB[1]]]$avgDetection[1],
                            estimatedParameters[[listTitlesZAB[2]]]$avgDetection[1],
                            estimatedParameters[[listTitlesZAB[3]]]$avgDetection[1],
                            estimatedParameters[[listTitlesZAB[4]]]$avgDetection[1]),
           
           avgDetectionSE = c(estimatedParameters[[listTitlesZAB[1]]]$avgDetectionSE[1],
                            estimatedParameters[[listTitlesZAB[2]]]$avgDetectionSE[1],
                            estimatedParameters[[listTitlesZAB[3]]]$avgDetectionSE[1],
                            estimatedParameters[[listTitlesZAB[4]]]$avgDetectionSE[1]))

knitr::kable(detOccZAB, format="markdown", caption = "Zabalo occupancy and detection estimates")
# save(detOccZAB, file = '../../Zabalo/Data/R Objects/detOccEstimatesZAB.RData')

```


\


\


### Estimate plotting
```{r}
# detOccZAB / detOccSGE for estimates and their standard errors
# bestModsFitListsZAB / bestModsFitListsSGE for the original fitLists that were predicted
# unmarkedPredDetZAB / unmarkedPredDetSGE for raw det/occ predictions across each site

# throw into one df

# Zabalo
speciesNames <- c("Collared peccary", "Red brocket", "Lowland paca", "Grey-winged trumpeter")
for (j in 1:length(speciesNames)) {
  unmarkedPredDetZAB[[j]]$Species <- speciesNames[j]
  unmarkedPredDetZAB[[j]]$Site <- 1:nrow(unmarkedPredDetZAB[[j]])
  unmarkedPredDetZAB[[j]]$Type <- "Detection"
  unmarkedPredDetZAB[[j]]$Community <- "Zábalo"

  unmarkedPredOccZAB[[j]]$Species <- speciesNames[j]
  unmarkedPredOccZAB[[j]]$Site <- 1:nrow(unmarkedPredOccZAB[[j]])
  unmarkedPredOccZAB[[j]]$Type <- "Occupancy"
  unmarkedPredOccZAB[[j]]$Community <- "Zábalo"

  unmarkedPredDetSGE[[j]]$Species <- speciesNames[j]
  unmarkedPredDetSGE[[j]]$Site <- 1:nrow(unmarkedPredDetSGE[[j]])
  unmarkedPredDetSGE[[j]]$Type <- "Detection"
  unmarkedPredDetSGE[[j]]$Community <- "Sinangoe"
  
  unmarkedPredOccSGE[[j]]$Species <- speciesNames[j]
  unmarkedPredOccSGE[[j]]$Site <- 1:nrow(unmarkedPredOccSGE[[j]])
  unmarkedPredOccSGE[[j]]$Type <- "Occupancy"
  unmarkedPredOccSGE[[j]]$Community <- "Sinangoe"
}


occupancyEstimates <- rbind(
  unmarkedPredOccZAB[['Collared peccary']][,c('Community', 'Site', 'Predicted', 'SE', 'lower', 'upper', 'Species')],
  unmarkedPredOccZAB[['Lowland paca']][,c('Community', 'Site', 'Predicted', 'SE', 'lower', 'upper', 'Species')],
  unmarkedPredOccZAB[['Grey-winged trumpeter']][,c('Community', 'Site', 'Predicted', 'SE', 'lower', 'upper', 'Species')],

  unmarkedPredOccSGE[['Collared peccary']][,c('Community', 'Site', 'Predicted', 'SE', 'lower', 'upper', 'Species')],
  unmarkedPredOccSGE[['Lowland paca']][,c('Community', 'Site', 'Predicted', 'SE', 'lower', 'upper', 'Species')],
  unmarkedPredOccSGE[['Grey-winged trumpeter']][,c('Community', 'Site', 'Predicted', 'SE', 'lower', 'upper', 'Species')]
  )
save(occupancyEstimates, file = "../Data/R Objects/occupancyEstimates.RData")

# work around to make x-axis labels with italics and divided into two lines
peccary <- ~ atop(paste("Collared peccary"), paste("(", italic("Dicotyles tajacu"), ")"))
paca <- ~ atop(paste("Lowland paca"), paste("(", italic("Cuniculus paca"), ")"))
trumpeter <- ~ atop(paste("Grey-winged trumpeter"), paste("(", italic("Psophia crepitans"), ")"))

# plot
ggplot(occupancyEstimates, aes(x = factor(Species, levels = unique(Species)),
                               y = Predicted,
                               fill = factor(Community, levels = unique(Community)))) +
  geom_boxplot(position = position_dodge(width = 0.8)) +
  scale_fill_manual(values = c("darkorange", "deepskyblue")) +
  labs(x = "Species", y = "Average occupancy probability") +
  theme_classic() +
  theme(text = element_text(family = "Times", colour = "black"),
        axis.text = element_text(colour = "black"),
        legend.title = element_blank(),
        axis.title.x = element_blank()) +
  scale_x_discrete(labels = c(peccary, paca, trumpeter))



```










